Spin canonical divisors of log stacky curves

### 2015-06-25 stacky_write_up/spin_cring.tex
editing order ram

Following Voight and Zureick-Brown \cite{vzb:stacky}, we examine a
much more general setting, generalizing Petri's theorem in many
directions. A divisor $\Delta \in d X$ is a {\bf log divisor} if
$\Delta = \sum_{i}^{}P_i \in \di X,$ with all $P_i$ distinct. Let
$(\sx,\Delta)$ denote a tame separably rooted curve over a
field $k$ so that $X$ is the coarse space of $\sx$, as defined in
\cite[Section 5.2]{vzb:stacky} so that $\di \sx = \di X \bigoplus_{i
= 1}^r \langle \frac{1}{e_i}P_i \rangle,$ with $e_i \in \BZ$. Let $K_
\sx = K_X + \sum_{i = 1}^{r}\frac{e_i - 1}{e_i}P_i.$ In this case, we
say $\sx$ has {\bf stabilizer order} $e_i$ at $P_i$. Call $\halfcan
\in \di \sx$ a {\bf log half-canonical divisor} on $(\sx,\Delta)$ if
$2\halfcan \sim K_\sx + \Delta$. If $X$ has genus $g$ and $\delta := \deg \Delta,$ then we
say $\sx$ has \textbf{signature} $\sigma = (g; e_1, \ldots, e_r; \delta)$. A
{\bf log spin curve} is a triple $(X, \Delta, \halfcan)$ where $(X,\Delta)$
and $\halfcan$ is a log half-canonical divisor on $(\sx,\Delta)$.
The central object of study in this paper is the {\bf log spin
canonical ring} of $(X,\Delta,L)$ is
\begin{align*}
	R(X,\Delta,L) = \bigoplus_{n \geq 0} H^0(X,nL)
\end{align*}

@@

\subsection{Definitions}
We reserve the notation $\halfcan$ for the halfcanonical divisor
where $2\halfcan \sim K_\sx + \Delta$.

@@

\iffalse{
However, before we can answer these general Lemmata, it is useful
to prove a nice result about minimal generation of ideals of
relations.

@@

%\begin{lem}
%\label{lem:minimal_quadratic}
%Suppose $k[x_1, \ldots, x_n]$ is a graded ring, not necessarily
%generated in degree 1, is equipped with a monomial ordering $\prec$.
 %Let $\phi:k[x_1, \ldots, x_n] \rightarrow B'$ be a map of graded
%rings with kernel $I'$, such that $I'$ is generated by elements $f_1,
%\ldots, f_j$, where $in_\prec(f_i) = x_i x_j,$ and no term of $f_i$
%is of the form $x_k$. Then, the elements $f_i$ determine minimal
%generators for $I$.
%\end{lem}
%\begin{proof}
%Regrade the ring $k[x_1, \ldots, x_n]$ so that all $x_i$ lie in
%degree 1. Then,
%\[
	%\phi : k[x_1, \ldots, x_n] \rightarrow B
%\]
%\noindent
%determines a map of rings, no longer necessarily graded. Consider
%the grlex monomial ordering $\prec$ on $k[x_1, \ldots, x_n]$.
%\todo{This ordering isn't quite right. 
%We need to preserve the ordering on quadratic terms}
%By
%assumption, the kernel $I$ is generated by elements whose initial
%terms have degree 2 and are all distinct. Therefore, $\dim_k (k[x_1,
%\ldots, x_n])_2 = \binom{n}{2} - j.$ This implies any set of
%generators for $I$ must have at least $j$ elements. Since $f_1,
%\ldots, f_j$ is such a set, it is minimal.
%\end{proof}
%
%\begin{rem}
%In particular, in the case of
%\[
	%\begin{tikzcd}
		%I\ar[hookrightarrow]{r}\ar[hookrightarrow]{d} & k[x_1, \ldots, x_n]
		%\ar[twoheadrightarrow]{r} \ar[hookrightarrow]{d} & B \ar[hookrightarrow]{d} \\
		%I' \ar[hookrightarrow]{r} & k[x_1, \ldots, x_n, y_1, \ldots, y_m] \ar[twoheadrightarrow]{r}& B'
	%\end{tikzcd}
%\]
%inducing
%\[
	%I/I'\hookrightarrow k[y_1, \ldots, y_m]\twoheadrightarrow B'/B
%\]
%\todo{how do we make this proof?}
%\end{rem}
\begin{lem}
\label{lem:minimal_quadratic}
Suppose $k[x_1, \ldots, x_n]\hookrightarrow k[x_1, \ldots, x_n, y_1, \ldots, y_m]$ be graded ring, not necessarily
generated in degree 1 that are equipped with monomial ordering $\prec$.
Let $\phi: k[x_1, \ldots, x_n] \twoheadrightarrow B, \phi':k[x_1, \ldots, x_n, y_1, \ldots, y_m]\twoheadrightarrow B'$ be maps of graded
rings with kernels $I \hookrightarrow I'$ such that the following diagram commutes:
\[
	\begin{tikzcd}
	I\ar[hookrightarrow]{r}\ar[hookrightarrow]{d} & k[x_1, \ldots, x_n]\ar[twoheadrightarrow]{r} \ar[hookrightarrow]{d} & B \ar[hookrightarrow]{d}\\
	I' \ar[hookrightarrow]{r} & k[x_1, \ldots, x_n, y_1, \ldots, y_m] \ar[twoheadrightarrow]{r}& B'
	\end{tikzcd}
\]
Further suppose that $I'$ is generated over $I$ by elements $f_1,
\ldots, f_j$ as a $k$-vector space, where $in_\prec(f_i) \in \{y_i x_j, y_i y_j\}$ and no monomial of $f_i$
is of the form $y_i$. Then, the elements $f_i$ determine minimal
generators for $I'$ over $I$.
\end{lem}

@@

\begin{rem}
\label{rem:minimal_quadratic_trivial_case}
It will be useful to use Lemma ~\ref{lem:minimal_quadratic} in the
case $m= 0$, in which case we find explicitly that $f_1, \ldots, f_r$
are $k$-minimal generators for $I'$ (over the trivial base vector
space). 
\end{rem}
With this result, we will be able to show that the sets of generators of the ideal of relations in many of the following inductive arguments are minimal.
}\fi

\ssec{Inductive Lemmata: Adding Points}
\label{ssec:add_pts}
In this section, we prove various inductive statements under the following setup:
Let $\halfcan'$ be $\mathbf{Q}$-divisor of $X$ (and often a log half-canonical divisor of some $\sx'$), satisfying certain conditions about $\deg(\lfloor d \halfcan'\rfloor)$ for various values of $d\in\mathbf{N}$ and certain saturation conditions. Let $\halfcan=\halfcan'+P$ for some $P$ possibly in the support of $\halfcan$.  Then we will explicitly describe elements that minimally generate\todo{check minimal generation actually works} $R_\halfcan$ over $\halfcan$' and initial terms of relations that minimally generate $\initial(I')$ over $\initial(I)$ (allowing the construction of a corresponding Gr\"{o}bner Basis).  The proofs of these Lemmas all follow similar patterns, so we will present a few \todo{give the precise number we show} and leave the rest to the reader.

@@

\begin{lem}
\label{lem:deg1-sat-ind}
Let $X$ be a genus $g$ curve with a $\mathbf{Q}$-divisor $\halfcan'$
satisfying $h^0(X, \lfloor{\halfcan'}\rfloor)\ge 1$. Suppose $P$ is not a base-point of $d\halfcan'$ for all $d\in \mathbf{N}^+$ meaning that $R_{\halfcan'}$ has generically chosen generators (in the necessary degrees)
$u, x_1, \ldots, x_m$ with $\ord_P(x_i)=0\; \forall x_i$, $\ord_P(u) = 0$, \todo{Aaron: Instead of having $\deg u = 0$, don't we only need that $\ord_P(u) = \lfloor \halfcan'|_P \rfloor$?} and $\deg(u)= 1$ when viewed as sections of $\so_{\halfcan'}$.  Suppose $u, x_1, \ldots, x_m$ generate $R_{\halfcan'}$ in degree at most $\bar{d}$ with relations generated
in degree at most $\bar{\tau}$.  Suppose $\halfcan = \halfcan' + \frac{\alpha}{\beta} P$
for some $\alpha,\beta \in \mathbf{N}$ such that
\begin{equation}
\label{eqn:deg1_sat_ind_dim}
	h^0(X, \lfloor{d\halfcan}\rfloor) = h^0(X,\lfloor d\halfcan'
	\rfloor) + \lfloor d\frac{\alpha} {\beta} \rfloor \text{ for all } d \in \mathbf{
	N} \text{ such that } d \ge \frac{\beta}{\alpha}.
\end{equation}
\label{eqn:deg1-sat-ind}
Let 
\[
	0 < \frac{c_1}{d_1} < \ldots < \frac{c_n}{d_n} = \frac{\alpha}{\beta}
\]
be the positive best lower approximations of $\frac{\alpha}{\beta}$.
Then

@@

In particular, if $\frac{\alpha}{\beta}\le 1$, then $I$ is minimally generated by elements with leading terms of the form $y_i x_j$ and $y_i y_j$.
%\item If $\gin_\prec(I')=\initial_\prec(I')$ then $\gin_\prec(I)=\initial_\prec(I)$.
%\item[(c)] A Gr\"{o}bner basis with the initial terms $y_i x_j$, $y_i y_j$,
%	and $(y_{\lfloor \frac{\alpha}{\beta} \rfloor})^{y_{\lfloor
%	\frac{\alpha}{\beta} \rfloor} + 1}$ (really the subset of these with positive subscripts) as shown above minimally
%generates $I'$.
\end{enumerate}
\end{lem}

@@

\begin{lem}\label{lem:relations_from_generators_induction} 
Suppose $\halfcan$ and $\halfcan'$ are $\mathbf{Q}$ divisors on a curve $X$ with $D=D'+\frac{\alpha}{\beta}P$.  Suppose $R_{\halfcan'}$ is generated by $x_1, \ldots, x_m$ and $R_{\halfcan}$ is minimally generated by $y_1, \ldots, y_n$ over $R_{\halfcan'}$; specifically, suppose there is a $k$-basis $S$ for $R_\halfcan$ over $R_{\halfcan'}$ such that $S$ consists only of monomials in $x_1, \ldots, x_m, y_1, \ldots, y_n$ and each $m\in S$ is not contained in $R_{\halfcan'}$.  
Let $I$ and $I'$ be the ideals of relations of $R_{\halfcan'}$ and $R_{\halfcan}$, for the given generating sets.  
Let $T\subseteq R_\halfcan - (S \cup R_{\halfcan'})$, such that any monomial of $(k[x_1, \ldots, x_m, y_1, \ldots, y_n])_{\ge 2}$ (the degrees at least 2 with respect to the regrading of each $x_1, \ldots, x_m, y_1, \ldots, y_n$) is either in $S$, $\langle T\rangle$, or $I' k[x_1, \ldots, x_m, y_1, \ldots, y_n]$.  Moreover, suppose there is some ordering $\prec$ such that if $T\prec S\prec k[x_1, \ldots, x_n]$ (that is, all elements of $T$ precede elements of $S$ which proceed monomials only in the $x_i$s). , then 
\begin{align*}
	\initial(I) & = \initial(I') k[x_1, \ldots, x_m, y_1, \ldots, y_n]\\
		     & + \langle T \rangle.
\end{align*}
\end{lem}
\begin{proof}
Suppose monomial $f\in T$ has a pole order $a$ at $P$.  Then since $S$ forms a $k$-basis of $R_{\halfcan}$ over $R_{\halfcan'}$, we can write $f + (\sum_{g\in S'} C_g g)+r$ for some finite subset $S'\subseteq S_{\deg(f)}$ and $r\in R_{\halfcan'}$.  This demonstrates that 
\begin{align*}
	\initial(I) & \supseteq \initial(I') k[x_1, \ldots, x_m, y_1, \ldots, y_n]\\
		     & + \langle T \rangle.
\end{align*}
Since every monomial of $k[x_1, \ldots, x_m, y_1, \ldots, y_n]$ either lies in $\langle T\rangle + \initial_\prec(I') k[x_1, \ldots, x_m, y_1, \ldots, y_n]$ or $S$, 
\begin{align*}
	\initial(I) & = \initial(I') k[x_1, \ldots, x_m, y_1, \ldots, y_n]\\
		     & + \langle T \rangle.
\end{align*}
\end{proof}

\begin{proof}[Proof of Lemma \ref{lem:deg1-sat-ind}]
By
our hypothesis (Equation ~\ref{eqn:deg1_sat_ind_dim}), for any $d
\in \mathbf{N}$ such that $\lfloor d \frac{ \alpha}{\beta} \rfloor > 0$,

@@

\iffalse{
\begin{lem}\label{lem:n-3s-admissible}
Fix a genus $g$, a log divisor $\Delta$, and a coarse space $X$. Suppose $3\le r\in \BN$ so that all stacky curves $\sx'$ with $r- 1$ ramified points of degree 3 over the coarse space $X$ have all subsets $J'$ of $\{e_1, \ldots, e_{r- 1}\}$ admissible in $L'$. Then if $\sx$ has coarse space $X$, any subset of $J$ of $\{e_1, \ldots, e_r\}$ (with all $e_i =3$) is admissible viewed in $L$.
\end{lem}
\begin{proof}
To show (Ad-i) and (Ad-ii) look at some $\sx'$ with $r- 1$ stacky points $'s=\{Q_1, \ldots, Q_{j - 1}, Q_{j + 1}, \ldots Q_r\}$ including a chosen $Q_i$ (and excluding some $Q_j\ne Q_i$). Then select $y_{e_r'}$ from the choice that makes the set $J'=\{i\}$ an admissible set in $\sx'$; this naturally can be seen inside of $R_{\sx}$ and satisfies (Ad-i). Furthermore, since $'s$ is an admissible set of $L'$, in particular, we must have (Ad-ii) satisfied so $\frac{-\ord_{Q_l}
^{\halfcan_X'}(y_i)}{\deg (y_i)} = 0$ for\todo{I'm confused how (Ad-ii) follows in genus 0?}

 follows immediately from the base-point freeness of $3\halfcan$ which we have for the following reasons in the various genera:
\begin{itemize}
\item When $g> 0$, $\deg(\lfloor 3 L\rfloor)\ge 3g-3+2\ge 2g$ (the added two comes from the fact that $r\ge 2$).
\item When $g= 0$, since $L'$ has a nontrivial admissible subset within $\{e_1, \ldots, e_{r- 1}\}$ satisfying (ad-i), we know $\deg(\lfloor 3\lfloor)\ge 0$, so it is base-point free.
\end{itemize}
\end{proof}
}\fi

@@

\begin{thm}
\label{thm:ram_order_ind}
Suppose $(\sx', \Delta, \halfcan')$ \todo{For some reason this $\Delta$ was set to 0. Was there any reason for this?} is a log spin curve with coarse
space $X'$ and signature $(g; e_1', \ldots, e_r'; \delta)$ and either $e_1' = \cdots = e_r' = 3$ or $(\sx',J)$ is admissible with generators $x_j, y_{i, e_i'} \in R' =
R_{L'}$ with $i \in J$ as in Definition ~\ref{defn:admissible}. Let
$(\sx, \Delta, \halfcan)$ be another log spin curve
with coarse space $X = X'$ and signature $(g; e_1, \ldots, e_r;
\delta)$ such that $e_i = e_i' + 2$ for all $i \in J$ and
$e_j = e_j'$ for $j \notin J$. Then the following are true:
\begin{enumerate}
	\item[(a)] For all $i \in J$, there exists $y_{i, e_i} \in
		H^0(\sx, e_i(K_\sx))$ so that
		\begin{align*}
			-\ord_{Q_i}
^{\halfcan_X'}(y_{i, e_i}) = \frac{e_i - 1}{2}
		\end{align*}
		and
		\begin{align*}
			\frac{-\ord_{Q_j}
^{\halfcan_X'}(y_{i, e_i})}{\deg (y_{i, e_i})} \leq 
\subhalf{
			e_j'} - \frac{1}{\deg(y_{i, e_i})e_j'}
		\end{align*}
		for all $j \in J$ with $j \neq i$.
	\item[(b)] The elements $y_{i, e_i'}^a y_{i, e_i}^b$ with $a \geq 
0,
		b > 0$ span $R$ over $R'$ and the elements $y_{i, e_i}$ minimally
		generate $R$ over $R'$.
	\item[(c)] Equip $k[y] = k[y_{i, e_i}]_{i \in J}$ and $k[x]$ with
		any graded monomial order and $k[y, x] = k[y] \otimes k[x]$ with
		block order. Let $R = k[y, x]/I.$ Then,
		\begin{align*}
			in_\prec(I) = in_\prec(I')k[x, y] + \langle y_{i, e_i}z \mid z 
			\neq y_{i, e_i}, y_{i, e_i'} \rangle
		\end{align*}
		as $z$ ranges over all generators of $R$.
	\item[(d)] Suppose $in_\prec(I')$ is minimally generated by
		products of two monomials and that for all $i \in J$, we have $e
		_i > \deg z$ for any generator $z$ of $R'.$ Then any set of
		minimal generators for $I'$ together with any set of relations 
as in 
		part (c) minimally generate $I$.
	\item[(e)] For any $W \subset J,$ the set $(\sx,W)$ is admissible.
\end{enumerate}
\end{thm}

@@

\section{High Genus}
\label{sec:g_high}
We now consider the case when the genus is at least 2. In this case, we are able to bound the degrees and relations of the half canonical ring $R_L$. In this section, we do not obtain explicit presentations of $R_L.$ In contrast, in Section ~\ref{sec:g_1} and Section ~\ref{sec:g_0} we will not only obtain bounds on the generators and relations, but also obtain presentations inductively. The tradeoff is that in the cases of genus 0 and 1, we will have to explicitly deal with base cases, making the induction more involved. We begin with the case that $g \geq 2$.

\ssec{Bounds on Generators and Relations in High Genus}

>>>>

Following Voight and Zureick-Brown \cite{vzb:stacky}, we examine a
much more general setting, generalizing Petri's theorem in many
directions. A divisor $\Delta \in d X$ is a {\bf log divisor} if
$\Delta = \sum_{i}^{}P_i \in \di X,$ with all $P_i$ distinct. Let
$(\sx,\Delta)$ denote a tame separably rooted curve over a
field $k$ so that $X$ is the coarse space of $\sx$, as defined in
\cite[Section 5.2]{vzb:stacky} so that $\di \sx = \di X \bigoplus_{i
= 1}^r \langle \frac{1}{e_i}P_i \rangle,$ with $e_i \in \BZ$. Let $K_
\sx = K_X + \sum_{i = 1}^{r}\frac{e_i - 1}{e_i}P_i.$ In this case, we
say $\sx$ has {\bf stabilizer order} $e_i$ at $P_i$. Call $\halfcan
\in \di \sx$ a {\bf log half-canonical divisor} on $(\sx,\Delta)$,
be a divisor $\halfcan \in \di \sx$ so that $2\halfcan \sim K_\sx +
\Delta.$ If $X$ has genus $g$ and $\delta = \deg \Delta,$ then we
say $\sx$ has \textbf{signature} $(g; e_1, \ldots, e_r;\delta)$. A
{\bf log spin curve} is a triple $(X,\Delta,\halfcan)$ where $(X,\Delta)$
and $\halfcan$ is a log half-canonical divisor on $(\sx,\Delta)$.
The central object of study in this paper is the {\bf log spin
canonical ring} of $(X,\Delta,L)$ is
\begin{align*}
	R(X,\Delta,L) = \bigoplus_{n \geq 0} H^0(X,nL)
\end{align*}

@@

\subsection{Definitions}
We reserve the notation $\halfcan$ for the halfcanonical divisor
where $\halfcan \sim $.

@@

However, before we can answer these general Lemmata, it is useful
to prove a nice result about minimal generation of ideals of
relations.

@@

%\begin{lem}
%\label{lem:minimal_quadratic}
%Suppose $k[x_1, \ldots, x_n]$ is a graded ring, not necessarily
%generated in degree 1, is equipped with a monomial ordering $\prec$.
 %Let $\phi:k[x_1, \ldots, x_n] \rightarrow B'$ be a map of graded
%rings with kernel $I'$, such that $I'$ is generated by elements $f_1,
%\ldots, f_j$, where $in_\prec(f_i) = x_i x_j,$ and no term of $f_i$
%is of the form $x_k$. Then, the elements $f_i$ determine minimal
%generators for $I$.
%\end{lem}
%\begin{proof}
%Regrade the ring $k[x_1, \ldots, x_n]$ so that all $x_i$ lie in
%degree 1. Then,
%\[
	%\phi : k[x_1, \ldots, x_n] \rightarrow B
%\]
%\noindent
%determines a map of rings, no longer necessarily graded. Consider
%the grlex monomial ordering $\prec$ on $k[x_1, \ldots, x_n]$.
%\todo{This ordering isn't quite right. 
%We need to preserve the ordering on quadratic terms}
%By
%assumption, the kernel $I$ is generated by elements whose initial
%terms have degree 2 and are all distinct. Therefore, $\dim_k (k[x_1,
%\ldots, x_n])_2 = \binom{n}{2} - j.$ This implies any set of
%generators for $I$ must have at least $j$ elements. Since $f_1,
%\ldots, f_j$ is such a set, it is minimal.
%\end{proof}
%
%\begin{rem}
%In particular, in the case of
%\[
	%\begin{tikzcd}
		%I\ar[hookrightarrow]{r}\ar[hookrightarrow]{d} & k[x_1, \ldots, x_n]
		%\ar[twoheadrightarrow]{r} \ar[hookrightarrow]{d} & B \ar[hookrightarrow]{d} \\
		%I' \ar[hookrightarrow]{r} & k[x_1, \ldots, x_n, y_1, \ldots, y_m] \ar[twoheadrightarrow]{r}& B'
	%\end{tikzcd}
%\]
%inducing
%\[
	%I/I'\hookrightarrow k[y_1, \ldots, y_m]\twoheadrightarrow B'/B
%\]
%\todo{how do we make this proof?}
%\end{rem}

\begin{lem}
\label{lem:minimal_quadratic}
Suppose $k[x_1, \ldots, x_n]\hookrightarrow k[x_1, \ldots, x_n, y_1, \ldots, y_m]$ be graded ring, not necessarily
generated in degree 1 that are equipped with monomial ordering $\prec$.
Let $\phi: k[x_1, \ldots, x_n] \twoheadrightarrow B, \phi':k[x_1, \ldots, x_n, y_1, \ldots, y_m]\twoheadrightarrow B'$ be maps of graded
rings with kernels $I \hookrightarrow I'$ such that the following diagram commutes:
\[
	\begin{tikzcd}
	I\ar[hookrightarrow]{r}\ar[hookrightarrow]{d} & k[x_1, \ldots, x_n]\ar[twoheadrightarrow]{r} \ar[hookrightarrow]{d} & B \ar[hookrightarrow]{d}\\
	I' \ar[hookrightarrow]{r} & k[x_1, \ldots, x_n, y_1, \ldots, y_m] \ar[twoheadrightarrow]{r}& B'
	\end{tikzcd}
\]
Further suppose that $I'$ is generated over $I$ by elements $f_1,
\ldots, f_j$ as a $k$-vector space, where $in_\prec(f_i) \in \{y_i x_j, y_i y_j\}$ and no monomial of $f_i$
is of the form $y_i$. Then, the elements $f_i$ determine minimal
generators for $I'$ over $I$.
\end{lem}

@@

\begin{rem}
\label{rem:minimal_quadratic_trivial_case}
It will be useful to use Lemma ~\ref{lem:minimal_quadratic} in the
case $m= 0$, in which case we find explicitly that $f_1, \ldots, f_r$
are $k$-minimal generators for $I'$ (over the trivial base vector
space). 
\end{rem}

With this result, we will be able to show that the sets of generators of the ideal of relations in many of the following inductive arguments are minimal.

\ssec{Inductive Lemmata: Adding Points}
\label{ssec:add_pts}
In this section, we prove various inductive statements under the following setup:
Let $\halfcan'$ be $\mathbb{Q}$-divisor of $X$ (and often a log half-canonical divisor of some $\sx'$), satisfying certain conditions about $\deg(\lfloor d \halfcan'\rfloor)$ for various values of $d\in\mathbb{N}$ and certain saturation conditions. Let $\halfcan=\halfcan'+P$ for some $P$ possibly in the support of $\halfcan$.  Then we will explicitly describe elements that minimally generate\todo{check minimal generation actually works} $R_\halfcan$ over $\halfcan$' and initial terms of relations that minimally generate $\initial(I')$ over $\initial(I)$ (allowing the construction of a corresponding Gr\"{o}bner Basis).  The proofs of these Lemmas all follow similar patterns, so we will present a few \todo{give the precise number we show} and leave the rest to the reader.

@@

\begin{lem}
\label{lem:deg1-sat-ind}
Let $X$ be a genus $g$ curve with a $\mathbb{Q}$-divisor $\halfcan'$
satisfying $h^0(X, \lfloor{\halfcan'}\rfloor)\ge 1$. Suppose $P$ is not a base-point of $d\halfcan'$ for all $d\in \mathbb{N}^+$ meaning that $R_{\halfcan'}$ has generically chosen generators (in the necessary degrees)
$u, x_1, \ldots, x_m$ with $\ord_P(x_i)=0\; \forall x_i$, $\ord_P(u) = 0$, \todo{Aaron: Instead of having $\deg u = 0$, don't we only need that $\ord_P(u) = \lfloor \halfcan'|_P \rfloor$?} and $\deg(u)= 1$ when viewed as sections of $\so_{\halfcan'}$.  Suppose $u, x_1, \ldots, x_m$ generate $R_{\halfcan'}$ in degree at most $\bar{d}$ with relations generated
in degree at most $\bar{\tau}$.  Suppose $\halfcan = \halfcan' + \frac{\alpha}{\beta} P$
for some $\alpha,\beta \in \mathbb{N}$ such that
\begin{equation}
\label{eqn:deg1_sat_ind_dim}
	h^0(X, \lfloor{d\halfcan}\rfloor) = h^0(X,\lfloor d\halfcan'
	\rfloor) + \lfloor d\frac{\alpha} {\beta} \rfloor \text{ for all } d \in \mathbb{
	N} \text{ such that } d \ge \frac{\beta}{\alpha}.
\end{equation}
\label{eqn:deg1-sat-ind}
Let 
\[
	0 < \frac{c_1}{d_1} < \ldots < \frac{c_n}{d_n} = \frac{\alpha}{\beta}
\]
be the positive best lower approximations of $\frac{\alpha}{\beta}$.
Then

@@

In particular, if $\frac{\alpha}{\beta}\le 1$, then $I$ is minimally generated by elements with leading terms of the form $y_i x_j$ and $y_i y_j$.
%\item If $\gin_\prec(I')=\initial_\prec(I')$ then $\gin_\prec(I)=\initial_\prec(I)$.
\item[(c)] A Gr\"{o}bner basis with the initial terms $y_i x_j$, $y_i y_j$,
	and $(y_{\lfloor \frac{\alpha}{\beta} \rfloor})^{y_{\lfloor
	\frac{\alpha}{\beta} \rfloor} + 1}$ (really the subset of these with positive subscripts) as shown above minimally
generates $I'$.
\end{enumerate}
\end{lem}

@@

\begin{lem}\label{lem:relations_from_generators_induction} 
Suppose $\halfcan$ and $\halfcan'$ are $\mathbf{Q}$ divisors on a curve $X$ with $D=D'+\frac{\alpha}{\beta}P$.  Suppose $R_{\halfcan'}$ is generated by $x_1, \ldots, x_m$ and $R_{\halfcan}$ is minimally generated by $y_1, \ldots, y_n$ over $R_{\halfcan'}$; specifically, suppose $S$ is a $k$ basis for $R_\halfcan$ over $R_{\halfcan'}$ such that $S$ consists only of monomials in $x_1, \ldots, x_m, y_1, \ldots, y_n$ and each $m\in S$ is not contained in $R_{\halfcan'}$.  Let $T\subseteq R_\halfcan - (S \cup R_{\halfcan'})$, such that any monomial of $(k[x_1, \ldots, x_m, y_1, \ldots, y_n])_{\ge 2}$ (the degrees at least 2 with respect to the regrading of each $x_1, \ldots, x_m, y_1, \ldots, y_n$) is either in $S$, $\langle T\rangle$, or $R_{\halfcan'}$.  Moreover, suppose there is some ordering $\prec$ such that if $f\in S$ and $g\not\in S, g\not\in R_{\halfcan'}$ is a quadratic monomial in $x_1, \ldots, x_m, y_1, \ldots, y_n$ in the same degree as $f$, then $g\prec f$.  Then if $I$ and $I'$ are the ideal of relations of $R_{\halfcan'}$ and $R_{\halfcan}$ with the given generating sets, then 
\begin{align*}
	\initial(I) & = \initial(I') k[x_1, \ldots, x_m, y_1, \ldots, y_n]\\
		     & + \langle T \rangle.
\end{align*}
Furthermore, if $T$ consists only of quadratic monomials, then $I$ is minimally generated over $I'$ by a Gr\"{o}bner Basis with an initial term for each element of $T$.
\end{lem}
\begin{proof}

\end{proof}

\begin{proof}[Proof of Lemma \ref{lem:deg1-sat-ind}]
By
our hypothesis (Equation ~\ref{eqn:deg1_sat_ind_dim}), for any $d
\in \mathbb{N}$ such that $\lfloor d \frac{ \alpha}{\beta} \rfloor > 0$,

@@

\begin{lem}\label{lem:n-3s-admissible}
Fix a genus $g$, a log divisor $\Delta$, and a coarse space $X$. Suppose $3\le r\in \BN$ so that all stacky curves $\sx'$ with $r- 1$ ramified points of degree 3 over the coarse space $X$ have all subsets $J'$ of $\{e_1, \ldots, e_{r- 1}\}$ admissible in $L'$. Then if $\sx$ has coarse space $X$, any subset of $J$ of $\{e_1, \ldots, e_r\}$ (with all $e_i =3$) is admissible viewed in $L$.
\end{lem}
\begin{proof}
To show (Ad-i) and (Ad-ii) look at some $\sx'$ with $r- 1$ stacky points $'s=\{Q_1, \ldots, Q_{j - 1}, Q_{j + 1}, \ldots Q_r\}$ including a chosen $Q_i$ (and excluding some $Q_j\ne Q_i$). Then select $y_{e_r'}$ from the choice that makes the set $J'=\{i\}$ an admissible set in $\sx'$; this naturally can be seen inside of $R_{\sx}$ and satisfies (Ad-i). Furthermore, since $'s$ is an admissible set of $L'$, in particular, we must have (Ad-ii) satisfied so $\frac{-\ord_{Q_l}
^{\halfcan_X'}(y_i)}{\deg (y_i)} = 0$ for\todo{I'm confused how (Ad-ii) follows in genus 0?}

 follows immediately from the base-point freeness of $3\halfcan$ which we have for the following reasons in the various genera:
\begin{itemize}
\item When $g> 0$, $\deg(\lfloor 3 L\rfloor)\ge 3g-3+2\ge 2g$ (the added two comes from the fact that $r\ge 2$).
\item When $g= 0$, since $L'$ has a nontrivial admissible subset within $\{e_1, \ldots, e_{r- 1}\}$ satisfying (ad-i), we know $\deg(\lfloor 3\lfloor)\ge 0$, so it is base-point free.
\end{itemize}
\end{proof}

@@

\begin{rem}
\label{rem:three-cases}
For the purposes of our induction, we will often be adding in a single 
stacky point with stabilizer order $3$. Say $(\sx,\Delta,\halfcan)$ is a log spin
curve with signature $\sigma = (g;e_1,\ldots, e_r,\delta) = (g;3,\ldots, 3,
\delta)$. We will need to deal with signatures $\sigma$ satisfying one of the following three cases:
\begin{enumerate}
	\item $g = 0, \delta = 0, $ and $r \geq 5$
	\item $g = 1, \delta = 0,$ and $ r \geq 2$
	\item $g \geq 2, \delta$ arbitrary, and $r \geq 1$.
\end{enumerate}
\end{rem}

\begin{thm}
\label{thm:ram_order_ind}
Suppose $(\sx', \Delta, \halfcan')$ \todo{For some reason this $\Delta$ was set to 0. Was there any reason for this?} is a log spin curve with coarse
space $X'$ and signature $(g; e_1', \ldots, e_r'; \delta)$ and either 
\begin{enumerate}
	\item  $(\sx',J)$ is admissible with generators $x_j, y_{i, e_i'} \in R' = R_{L'}$ with $i \in J$ as in Definition ~\ref{defn:admissible}
	\item or $e_1' = \cdots = e_r' = 3$ and $r \geq 2$ or $g \geq 2$, and let $y_{1, 3}$ be a rational section of $\sco(\halfcan_X)$ so that $\ord_{P_i}^{\halfcan_X'}(y_{1,3}) = 1$ at $P_i$ for all $i = 1,\ldots, r$.
\end{enumerate}
Let
$(\sx, \Delta, \halfcan)$ be another log spin curve
with coarse space $X = X'$ and signature $(g; e_1, \ldots, e_r;
\delta)$ such that $e_i = e_i' + 2$ for all $i \in J$ and
$e_j = e_j'$ for $j \notin J$. Then the following are true:
\begin{enumerate}
	\item[(a)] For all $i \in J$, there exists $y_{i, e_i} \in
		H^0(\sx, e_i(K_\sx))$ so that
		\begin{align*}
			-\ord_{Q_i}
^{\halfcan_X'}(y_{i, e_i}) = \frac{e_i - 1}{2}
		\end{align*}
		and
		\begin{align*}
			\frac{-\ord_{Q_j}
^{\halfcan_X'}(y_{i, e_i})}{\deg (y_{i, e_i})} \leq 
\subhalf{
			e_j'} - \frac{1}{\deg(y_{i, e_i})e_j'}
		\end{align*}
		for all $j \in J$ with $j \neq i$.
	\item[(b1)] If $(\sx',\halfcan',J)$ is admissible, then $y_{i, e_i'}^a y_{i, e_i}^b$ with $a \geq 
0,
		b > 0$ span $R$ over $R'$ and the elements $y_{i, e_i}$ minimally
		generate $R$ over $R'$.
	\item[(b2)] If $(\sx',\halfcan',J)$ is not admissible, but $\{e_1,\ldots, e_n\} = \{3\},$ the elements $y_{i, e_i}$ minimally
		generate $R$ over $R'$.
	\item[(c1)] If $(\sx',\halfcan',J)$ is admissible, equip $k[y] = k[y_{i, e_i}]_{i \in J}$ and $k[x]$ with
		any graded monomial order and $k[y, x] = k[y] \otimes k[x]$ with
		block order. Let $R = k[y, x]/I.$ Then,
		\begin{align*}
			in_\prec(I) = in_\prec(I')k[x, y] + \langle y_{i, e_i}z \mid z 
			\neq y_{i, e_i}, y_{i, e_i'} \rangle
		\end{align*}
		as $z$ ranges over all generators of $R$.
	\item[(c2)]  If $(\sx',\halfcan',J)$ is not admissible, equip $k[y] = k[y_{i, e_i}]_{i \in J}$ and $k[x]$ with
		any graded monomial order and $k[y, x] = k[y] \otimes k[x]$ with
		block order. Let $R = k[y, x]/I.$ Then,
		\begin{align*}
			in_\prec(I) = in_\prec(I')k[x, y] + \langle y_{i, e_i}z \mid z 
			\neq y_{i, e_i}, y_{i, e_i'} \rangle
		\end{align*}
		as $z$ ranges over all generators of $R$.

	\item[(d)] Suppose $in_\prec(I')$ is minimally generated by
		products of two monomials and that for all $i \in J$, we have $e
		_i > \deg z$ for any generator $z$ of $R'.$ Then any set of
		minimal generators for $I'$ together with any set of relations 
as in 
		part (c) minimally generate $I$.
	\item[(e)] For any $W \subset J,$ the set $(\sx,W)$ is admissible.
\end{enumerate}
\end{thm}

@@

\section{High genus}
\label{sec:g_high}
We now consider the case when the genus is at least 2. In this case, we are able to bound the degrees and relations of the half canonical ring $R_L$. In this section, we do not obtain explicit presentations of $R_L.$ In contrast, in Section ~\ref{sec:g_1} and Section ~\ref{sec:g_0} we will not only obtain bounds on the generators and relations, but also obtain presentations inductively. The tradeoff is that in the cases of genus 0 and 1, we will have to explicitly deal with base cases, making the induction more involved. We begin with the case that $g \geq 2$.

\ssec{Bounds on Generators and Relations in high genus}
